Mental Health Factors and Covid

### 2025-03-15 code/processing-code/processing.qmd
Part 3 commit, complete eda and start analysis

---
title: "R Coding Exercise"
---

@@

Now, loading data using the here package.
```{r}
here() #set working directory
data_original <- readRDS(here("data","raw-data", "NHIS_COVID.rds"))
names(data_original)
```

Selecting variables we need will make the dataset smaller and quicker to work with. Note it is renamed at each step for reproducibility. 
```{r}
data1 <- data_original %>%
  select(STRATA, PSU, PERNUM, SAMPWEIGHT, AGE, PA18AERSTR, HRSLEEP, DEPFREQ, PHQSLEEP, CMPSUPPORT, CVDTESTRSLT)
```

@@

We will create binary vairables in a new dataset. For each variable, those who answered NA, 0, 996, 997, 998, 999 will be converted to NA for the remainder of that variable for the continuation of the analysis.
```{r}
unique(data1$CVDTESTRSLT)
data2 <- data1 %>%
  mutate(
    PA18AERSTR = ifelse(PA18AERSTR %in% c(0, 7, 8, 9), NA, PA18AERSTR), #put NA, 0, 6, 7, 8, 9 to NA
    EXERCISE = if_else(PA18AERSTR %in% c(2,3,4), 1, 0, missing = NA_real_) #create EXERCISE vairable, 1 if guidelines by Am Heart Assoc met for aerobics, strength, or both, 0 if not met
    ) %>%
    mutate(
    AGE = ifelse(AGE %in% c(997, 999), NA, AGE),  #invalid ages to NA
    SLEEP = case_when( #Based on age, amount of sleep required from https://www.nhlbi.nih.gov/health/sleep/how-much-sleep#:~:text=Experts%20recommend%20that%20adults%20sleep,or%20more%20hours%20a%20night.
      AGE < 1  ~ if_else(HRSLEEP >= 12 & HRSLEEP <= 16, 1, 0, missing = NA_real_),
      AGE >= 1 & AGE < 3       ~ if_else(HRSLEEP >= 11 & HRSLEEP <= 14, 1, 0, missing = NA_real_),
      AGE >= 3 & AGE < 6       ~ if_else(HRSLEEP >= 10 & HRSLEEP <= 13, 1, 0, missing = NA_real_),
      AGE >= 6 & AGE < 13      ~ if_else(HRSLEEP >= 9 & HRSLEEP <= 12, 1, 0, missing = NA_real_),
      AGE >= 13 & AGE <= 18    ~ if_else(HRSLEEP >= 8 & HRSLEEP <= 10, 1, 0, missing = NA_real_),
      TRUE                     ~ NA_real_  #default NA for unspecified ages
    )) %>%
  mutate(
    DEPRESSED = case_when(
      DEPFREQ %in% c(1, 2) ~ 1, #daily and weekly is considered depressed
      DEPFREQ %in% c(3, 4, 5)    ~ 0, #monthly and a few times a year and never are considered not depressed
      DEPFREQ %in% c(0, 7, 8, 9) ~ NA_real_,#NIU & Unknowns are NA
      TRUE ~ NA_real_ #default NA for unexpected values
    )) %>%
  mutate(
    TROUBLE_SLEEPING = case_when(
      PHQSLEEP %in% c(1, 2, 3) ~ 1, #several days, more than half days, nearly every day are trouble sleeping
      PHQSLEEP == 0            ~ 0,  #not at all is no trouble sleeping
      PHQSLEEP %in% c(6, 7, 8, 9) ~ NA_real_,  #NIU & Unknowns are NA
      TRUE ~ NA_real_  #default NA for unexpected values
    )) %>%
  mutate(
    SOCIAL = case_when(
      CMPSUPPORT == 1 ~ 0,   #more social and emotional support
      CMPSUPPORT == 2 ~ 1,  #less social and emotional support
      CMPSUPPORT == 3 ~ 0,   #about the same
      CMPSUPPORT %in% c(0, 7, 8, 9) ~ NA_real_,  # NIU & Unknowns → NA
      TRUE ~ NA_real_  #default NA for unexpected values
    )) %>%
  mutate(
    COVID = case_when(
      CVDTESTRSLT == 2 ~ 1,  #yes, had COVID
      CVDTESTRSLT == 1 ~ 0,  #no, did not have COVID
      CVDTESTRSLT %in% c(0, 3, 7, 8, 9) ~ NA_real_,  #NIU, did not receive results, unknowns, and NA are NA
      TRUE ~ NA_real_  #default NA for unexpected values
    ))

@@

Now, I will make plots to explore how these look to ensure there's no problems. I used ChatGPT to help make the table. Each row doesn't add up to 1, this is because the yes/no adds up to 1, and the NA and not NA adds up to 1. Notably, some of these vairables have high NA porportions, but I can't remove them from the set because that would affect the survey design variables, but I will keep it in mind for the rest of the analysis should there be any issues such as singleton strata varibales etc.
```{r}
hist(data2$SLEEP) #histograms of 0 and 1 for each variable
hist(data2$EXERCISE)
hist(data2$DEPRESSED)
hist(data2$TROUBLE_SLEEPING)
hist(data2$SOCIAL)
hist(data2$COVID)

#summarize EXERCISE
summary_exercise <- data2 %>%
  summarise(
    Variable = "EXERCISE",
    Prop_1 = mean(EXERCISE == 1, na.rm = TRUE),
    Prop_0 = mean(EXERCISE == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(EXERCISE))
  )

#summarize SLEEP
summary_sleep <- data2 %>%
  summarise(
    Variable = "SLEEP",
    Prop_1 = mean(SLEEP == 1, na.rm = TRUE),
    Prop_0 = mean(SLEEP == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(SLEEP))
  )

#summarize DEPRESSED
summary_depressed <- data2 %>%
  summarise(
    Variable = "DEPRESSED",
    Prop_1 = mean(DEPRESSED == 1, na.rm = TRUE),
    Prop_0 = mean(DEPRESSED == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(DEPRESSED))
  )

#summarize TROUBLE SLEEPING
summary_trouble_sleeping <- data2 %>%
  summarise(
    Variable = "TROUBLE SLEEPING",
    Prop_1 = mean(TROUBLE_SLEEPING == 1, na.rm = TRUE),
    Prop_0 = mean(TROUBLE_SLEEPING == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(TROUBLE_SLEEPING))
  )

#summarize SOCIAL
summary_social <- data2 %>%
  summarise(
    Variable = "SOCIAL",
    Prop_1 = mean(SOCIAL == 1, na.rm = TRUE),
    Prop_0 = mean(SOCIAL == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(SOCIAL))
  )

#summarize COVID
summary_covid <- data2 %>%
  summarise(
    Variable = "COVID",
    Prop_1 = mean(COVID == 1, na.rm = TRUE),
    Prop_0 = mean(COVID == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(COVID))
  )

#combine all summaries and convert to gt table
summary_table <- bind_rows(
  summary_exercise, 
  summary_sleep, 
  summary_depressed, 
  summary_trouble_sleeping, 
  summary_social, 
  summary_covid
) %>%
  gt() %>%
  tab_header(
    title = "Proportions of 1, 0, and NA for Various Variables"
  )

#print the combined table
summary_table

#save the table as a PNG image
gtsave(summary_table, here("data", "processed-data", "figures", "summary_table.png"))
```

>>>>

---
title: "Processing Code"
---

@@

Now, loading data using the here package.
```{r}
here() #set working directory
data_original <- readRDS(here("data","raw-data", "NHIS_COVID.rds"))
data1 <- labelled::remove_val_labels(data_original) #removes labels from haven package which cause problems
```

Selecting variables we need will make the dataset smaller and quicker to work with. Note it is renamed at each step for reproducibility. 
```{r}
names(data_original) #view names of variables
data1 <- data_original %>%
  select(STRATA, PSU, PERNUM, SAMPWEIGHT, AGE, PA18AERSTR, HRSLEEP, DEPFREQ, PHQSLEEP, CMPSUPPORT, CVDTESTRSLT)
```

@@

We will create binary vairables in a new dataset. For each variable, those who answered NA, 0, 996, 997, 998, 999 will be converted to NA for the remainder of that variable for the continuation of the analysis.
```{r}
data2 <- data1 %>%
  mutate(
    PA18AERSTR = ifelse(PA18AERSTR %in% c(0, 7, 8, 9), NA, PA18AERSTR), #put NA, 0, 6, 7, 8, 9 to NA
    EXERCISE = if_else(PA18AERSTR %in% c(2,3,4), 1, 0, missing = NA_real_) #create EXERCISE variable, 1 if guidelines by Am Heart Assoc met for aerobics, strength, or both, 0 if not met
    ) %>%
    mutate(
    AGE = ifelse(AGE %in% c(997, 999), NA, AGE),  #invalid ages to NA
    SLEEP = case_when( #Based on age, amount of sleep required from https://www.nhlbi.nih.gov/health/sleep/how-much-sleep#:~:text=Experts%20recommend%20that%20adults%20sleep,or%20more%20hours%20a%20night.
      AGE < 1  ~ if_else(HRSLEEP >= 12 & HRSLEEP <= 16, 1, 0, missing = NA_real_),
      AGE >= 1 & AGE < 3       ~ if_else(HRSLEEP >= 11 & HRSLEEP <= 14, 1, 0, missing = NA_real_),
      AGE >= 3 & AGE < 6       ~ if_else(HRSLEEP >= 10 & HRSLEEP <= 13, 1, 0, missing = NA_real_),
      AGE >= 6 & AGE < 13      ~ if_else(HRSLEEP >= 9 & HRSLEEP <= 12, 1, 0, missing = NA_real_),
      AGE >= 13 & AGE <= 18    ~ if_else(HRSLEEP >= 8 & HRSLEEP <= 10, 1, 0, missing = NA_real_),
      TRUE                     ~ NA_real_  #default NA for unspecified ages
    )) %>%
  mutate(
    DEPRESSED = case_when(
      DEPFREQ %in% c(1, 2) ~ 1, #daily and weekly is considered depressed
      DEPFREQ %in% c(3, 4, 5)    ~ 0, #monthly and a few times a year and never are considered not depressed
      DEPFREQ %in% c(0, 7, 8, 9) ~ NA_real_,#NIU & Unknowns are NA
      TRUE ~ NA_real_ #default NA for unexpected values
    )) %>%
  mutate(
    TROUBLE_SLEEPING = case_when(
      PHQSLEEP %in% c(1, 2, 3) ~ 1, #several days, more than half days, nearly every day are trouble sleeping
      PHQSLEEP == 0            ~ 0,  #not at all is no trouble sleeping
      PHQSLEEP %in% c(6, 7, 8, 9) ~ NA_real_,  #NIU & Unknowns are NA
      TRUE ~ NA_real_  #default NA for unexpected values
    )) %>%
  mutate(
    SOCIAL = case_when(
      CMPSUPPORT == 1 ~ 0,   #more social and emotional support
      CMPSUPPORT == 2 ~ 1,  #less social and emotional support
      CMPSUPPORT == 3 ~ 0,   #about the same
      CMPSUPPORT %in% c(0, 7, 8, 9) ~ NA_real_,  # NIU & Unknowns → NA
      TRUE ~ NA_real_  #default NA for unexpected values
    )) %>%
  mutate(
    COVID = case_when(
      CVDTESTRSLT == 2 ~ 1,  #yes, had COVID
      CVDTESTRSLT == 1 ~ 0,  #no, did not have COVID
      CVDTESTRSLT %in% c(0, 3, 7, 8, 9) ~ NA_real_,  #NIU, did not receive results, unknowns, and NA are NA
      TRUE ~ NA_real_  #default NA for unexpected values
    ))

@@

### 2025-03-15 products/manuscript/Manuscript.qmd
Part 3 commit, complete eda and start analysis

---
title: "Learning Influenza Forecasting"
author: "Annalise Cramer"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(survey)
here()
```

@@

## General Background Information
_Provide enough background on your topic that others can understand the why and how of your analysis_

## Description of data and data source
_Describe what the data is, what it contains, where it is from, etc. Eventually this might be part of a methods section._

@@

Examples of reproducible research projects can for instance be found in [@mckay2020; @mckay2020a].

@@

Data for this project is survey data collected from the National Health Interview Survey, produced by IPUMS through the University of Minnesota. This data was collected among United States residents of all ages and genders from 2019 - 2022 in the United States. There's 151406 observations and 47 vairables.

Survey design variables were used and new binary variables were created from other variables.

@@

Sometimes you might want to show a schematic diagram/figure that was not created with code (if you can do it with code, do it). @fig-schematic is an example of some - completely random/unrelated - schematic that was generated with Biorender.
We store those figures in the `assets` folder.

```{r}
#| label: fig-schematic
#| fig-cap: "A figure that is manually generated and shows some overview/schematic. This has nothing to do with the data, it's just a random one from one of our projects I found and placed here."
#| echo: FALSE
knitr::include_graphics(here("assets","antigen-recognition.png"))
```

## Data aquisition
This data was obtained from IPUMS, used with permission.

## Data import and cleaning
_Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along._

Raw data called NHIS_COVID.rds, sits with the data folder, in a a subfolder called raw data. The processed data, called data3.rds, is within the data folder in a subfolder called processed-data. The code to clean and explore and process this dadta is within the code folder, in the processing-code subfolder, called data-cleaning-project.qmd.

The raw data was loaded, and necessary variables and survery design variables were selected. After exploring each variable, new binary variables were created.

For now, let us load the processed data. Here's a histogram of the processed outcome vairable, which represents whether or not an indivudal has ever tested postive for COVID. Histograms of all vairables are available in the data-cleaning-project.qmd file, but will not be shown here for the sake of space.
```{r}
library(here)
data <- read_rds(here("data", "processed-data", "data3.rds"))
hist(data$COVID)
```

@@

@@

@@

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table, proportions of 0 compared to 1, and proportion NA to not NA."
#| echo: FALSE
here()
knitr::include_graphics(here("data","processed-data", "figures", "summary_table.png"))
```

@@

@fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
knitr::include_graphics(here("results","figures","height-weight-stratified.png"))
```

@@

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","tables","resulttable2.rds"))
knitr::kable(resulttable2)
```

>>>>

---
title: "Mental Health Factors and Covid"
author: "Annalise Cramer"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
#bibliography: ../../assets/dataanalysis-references.bib
#csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(tableone)
library(survey)
library(gt)
here()
```

@@

## General Background Information

During the SARS-CoV pandemic, methods implemented to control the transmission of the disease had broader societal impacts. A common complaint surrounding social distancing and quarantine policies is the effects on mental health 1. This study aims to better understand the associations between mental health factors and contracting covid. Using data from the National Health Interview Surveys collected during the SARS-CoV-2 pandemic, simple and multiple regression models are created.

Cite this properly later:
1.) https://www.tandfonline.com/doi/full/10.1080/09638237.2020.1757052

## Description of data and data source

Data for this project is survey data collected from the National Health Interview Survey, produced by IPUMS through the University of Minnesota. This data was collected among United States residents of all ages and genders from 2019 - 2022 in the United States.

@@

@@

There's 151406 observations and 47 variables.

Survey design variables were used and new binary variables were created from other variables. Using complex survey design variables, a descriptive table was created.

@@

Sometimes you might want to show a schematic diagram/figure that was not created with code (if you can do it with code, do it). fig-schematic is an example of some - completely random/unrelated - schematic that was generated with Biorender.
We store those figures in the `assets` folder.

```{r}
#| label: fig-schematic
#| fig-cap: "A figure that is manually generated and shows some overview/schematic. This has nothing to do with the data, it's just a random one from one of our projects I found and placed here."
#| echo: FALSE
#knitr::include_graphics(here("assets","antigen-recognition.png"))
```

## Data aquisition

This data was obtained from IPUMS, used with permission.

## Data import and cleaning

The following code details the data cleaning process. Labels are removed from the data to make it easier to work with to create models later in the process. Variables needed are selected, then a series of binary varibales are created. Additional details are available in the processing folder.
```{r}
here() #set working directory
data_original <- readRDS(here("data","raw-data", "NHIS_COVID.rds"))
data1 <- labelled::remove_val_labels(data_original) #removes labels from haven package which cause problems

data1 <- data_original %>%
  select(STRATA, PSU, PERNUM, SAMPWEIGHT, AGE, PA18AERSTR, HRSLEEP, DEPFREQ, PHQSLEEP, CMPSUPPORT, CVDTESTRSLT)

data2 <- data1 %>%
  mutate(
    PA18AERSTR = ifelse(PA18AERSTR %in% c(0, 7, 8, 9), NA, PA18AERSTR), #put NA, 0, 6, 7, 8, 9 to NA
    EXERCISE = if_else(PA18AERSTR %in% c(2,3,4), 1, 0, missing = NA_real_) #create EXERCISE variable, 1 if guidelines by Am Heart Assoc met for aerobics, strength, or both, 0 if not met
    ) %>%
    mutate(
    AGE = ifelse(AGE %in% c(997, 999), NA, AGE),  #invalid ages to NA
    SLEEP = case_when( #Based on age, amount of sleep required from https://www.nhlbi.nih.gov/health/sleep/how-much-sleep#:~:text=Experts%20recommend%20that%20adults%20sleep,or%20more%20hours%20a%20night.
      AGE < 1  ~ if_else(HRSLEEP >= 12 & HRSLEEP <= 16, 1, 0, missing = NA_real_),
      AGE >= 1 & AGE < 3       ~ if_else(HRSLEEP >= 11 & HRSLEEP <= 14, 1, 0, missing = NA_real_),
      AGE >= 3 & AGE < 6       ~ if_else(HRSLEEP >= 10 & HRSLEEP <= 13, 1, 0, missing = NA_real_),
      AGE >= 6 & AGE < 13      ~ if_else(HRSLEEP >= 9 & HRSLEEP <= 12, 1, 0, missing = NA_real_),
      AGE >= 13 & AGE <= 18    ~ if_else(HRSLEEP >= 8 & HRSLEEP <= 10, 1, 0, missing = NA_real_),
      TRUE                     ~ NA_real_  #default NA for unspecified ages
    )) %>%
  mutate(
    DEPRESSED = case_when(
      DEPFREQ %in% c(1, 2) ~ 1, #daily and weekly is considered depressed
      DEPFREQ %in% c(3, 4, 5)    ~ 0, #monthly and a few times a year and never are considered not depressed
      DEPFREQ %in% c(0, 7, 8, 9) ~ NA_real_,#NIU & Unknowns are NA
      TRUE ~ NA_real_ #default NA for unexpected values
    )) %>%
  mutate(
    TROUBLE_SLEEPING = case_when(
      PHQSLEEP %in% c(1, 2, 3) ~ 1, #several days, more than half days, nearly every day are trouble sleeping
      PHQSLEEP == 0            ~ 0,  #not at all is no trouble sleeping
      PHQSLEEP %in% c(6, 7, 8, 9) ~ NA_real_,  #NIU & Unknowns are NA
      TRUE ~ NA_real_  #default NA for unexpected values
    )) %>%
  mutate(
    SOCIAL = case_when(
      CMPSUPPORT == 1 ~ 0,   #more social and emotional support
      CMPSUPPORT == 2 ~ 1,  #less social and emotional support
      CMPSUPPORT == 3 ~ 0,   #about the same
      CMPSUPPORT %in% c(0, 7, 8, 9) ~ NA_real_,  # NIU & Unknowns → NA
      TRUE ~ NA_real_  #default NA for unexpected values
    )) %>%
  mutate(
    COVID = case_when(
      CVDTESTRSLT == 2 ~ 1,  #yes, had COVID
      CVDTESTRSLT == 1 ~ 0,  #no, did not have COVID
      CVDTESTRSLT %in% c(0, 3, 7, 8, 9) ~ NA_real_,  #NIU, did not receive results, unknowns, and NA are NA
      TRUE ~ NA_real_  #default NA for unexpected values
    ))
```

@@

We will begin with exploratory tables to explore proportions of NA answers, and generate early estimates.

Our first figure with be a discriptive table stratified by COVID status, with estimates and 95% CIs.

Next, we will construct simple models before moving onto adjusted models.

@@

The first table below details the proportion of NAs for each mental health variable. We can see this is a little bit high, which may affect analysis later on. Histograms of each variable are available in the eda folder.

The second table shows proportions calculated using complex survey design variables.

```{r}
data <- data2
#summarize EXERCISE
summary_exercise <- data %>%
  summarise(
    Variable = "EXERCISE",
    Prop_1 = mean(EXERCISE == 1, na.rm = TRUE),
    Prop_0 = mean(EXERCISE == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(EXERCISE))
  )

#summarize SLEEP
summary_sleep <- data %>%
  summarise(
    Variable = "SLEEP",
    Prop_1 = mean(SLEEP == 1, na.rm = TRUE),
    Prop_0 = mean(SLEEP == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(SLEEP))
  )

#summarize DEPRESSED
summary_depressed <- data %>%
  summarise(
    Variable = "DEPRESSED",
    Prop_1 = mean(DEPRESSED == 1, na.rm = TRUE),
    Prop_0 = mean(DEPRESSED == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(DEPRESSED))
  )

#summarize TROUBLE SLEEPING
summary_trouble_sleeping <- data %>%
  summarise(
    Variable = "TROUBLE SLEEPING",
    Prop_1 = mean(TROUBLE_SLEEPING == 1, na.rm = TRUE),
    Prop_0 = mean(TROUBLE_SLEEPING == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(TROUBLE_SLEEPING))
  )

#summarize SOCIAL
summary_social <- data %>%
  summarise(
    Variable = "SOCIAL",
    Prop_1 = mean(SOCIAL == 1, na.rm = TRUE),
    Prop_0 = mean(SOCIAL == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(SOCIAL))
  )

#summarize COVID
summary_covid <- data %>%
  summarise(
    Variable = "COVID",
    Prop_1 = mean(COVID == 1, na.rm = TRUE),
    Prop_0 = mean(COVID == 0, na.rm = TRUE),
    Prop_NA = mean(is.na(COVID))
  )

#combine all summaries and convert to gt table
summary_table <- bind_rows(
  summary_exercise, 
  summary_sleep, 
  summary_depressed, 
  summary_trouble_sleeping, 
  summary_social, 
  summary_covid
) %>%
  gt() %>%
  tab_header(
    title = "Proportions of 1, 0, and NA for Various Variables"
  )

#print the combined table
summary_table

#list variables
varstable1 = c("EXERCISE", "SLEEP", "DEPRESSED", "TROUBLE_SLEEPING", 
             "SOCIAL", "COVID")

#list categories
cat_vartab1 = c("EXERCISE", "SLEEP", "DEPRESSED", "TROUBLE_SLEEPING", 
             "SOCIAL", "COVID")

#use function to make table
Tab1 = CreateTableOne(vars = varstable1, factorVars = cat_vartab1, data = data)

# Convert the TableOne object to a data frame
tab1_df <- as.data.frame(print(Tab1, showAllLevels = TRUE, quote = FALSE, noSpaces = TRUE))

# Clean up row names
tab1_df <- tibble::rownames_to_column(tab1_df, "Variable")

# More advanced formatting
tab1_gt <- gt(tab1_df) %>%
  # Add a title
  tab_header(
    title = md("**COVID test status and Mental Health Factors**"),
    subtitle = "Survey Results Summary"
  ) %>%
  # Format the columns
  fmt_percent(
    columns = contains("%"),
    decimals = 1
  ) %>%
  # Group the variables
  tab_row_group(
    label = "COVID Status",
    rows = contains("COVID")
  ) %>%
  tab_row_group(
    label = "Mental Health Indicators",
    rows = contains(c("DEPRESSED", "TROUBLE_SLEEPING"))
  ) %>%
  tab_row_group(
    label = "Lifestyle Factors",
    rows = contains(c("EXERCISE", "SLEEP", "SOCIAL"))
  ) %>%
  # Style the table
  tab_style(
    style = cell_fill(color = "#e6f3ff"),
    locations = cells_row_groups()
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_row_groups()
  ) %>%
  # Add footnotes if needed
  tab_footnote(
    footnote = "Percentages may not sum to 100% due to rounding",
    locations = cells_column_labels(columns = contains("%"))
  ) %>%
  # Adjust column widths
  cols_width(
    Variable ~ px(250),
    everything() ~ px(120)
  )

tab1_gt
```

@@

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Table. 1. Mental health characteristics among Americans from 2019-2022, by SARS-CoV-2 test result status, NHIS"
#| echo: FALSE
here()
knitr::include_graphics(here("results","figures", "result_table1.png"))
```

@@

fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
#knitr::include_graphics(here("results","figures","height-weight-stratified.png"))
```

@@

Example tbl-resulttable2 shows a summary of a linear model fit.
